\documentclass[12pt]{article}

\linespread{1}

\makeatletter
\renewcommand*{\p@section}{\S\,}
\renewcommand*{\p@subsection}{\S\,}
\renewcommand*{\p@subsubsection}{\S\,}
\makeatother

\usepackage[english]{babel}
\usepackage{color}
\usepackage{enumerate}
\usepackage[textheight = 675pt]{geometry}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref} \hypersetup{colorlinks=true, urlcolor=blue}
\usepackage{ifpdf}
\usepackage{yfonts}

\pagestyle{fancy}
\setlength{\headheight}{10pt}
\lhead{M.B. Adams *}
\chead{\emph{University of Rochester}}
\rhead{Head TA Duties}
\lfoot{* e-mail: \href{mailto:madams@pas.rochester.edu}{madams@pas.rochester.edu} }
\title{PHY12XP Head Teaching Assistant Duties}
\author{Marissa B. Adams}
\date{\today}

\begin{document}

\maketitle

\thispagestyle{fancy}

\section{Introduction}

\indent If you are reading this document perhaps you have been selected to manage and run the Mastery/Self-Paced (MSP) Physics courses at the University of Rochester. There are generally two courses that fit this format: PHY122P (\emph{Electricity and Magnetism for Scientists and Engineers}), and PHY121P (\emph{Mechanics for Scientists and Engineers}). The former generally takes place during the Fall semesters, and the latter, the Spring. Both courses are freshman-sophomore level physics courses that are generally aimed at engineering students. Both courses follow the framework under the MSP philosophy. 

\indent One stark difference is that PHY122P has 12 modules, while PHY121P has 13. The number of modules is tried and true, however there is much room for course development, and statistical analysis in a MSP course. It is up to the professor to decide if they would like to make some changes during before the semester begins. This document will detail the general flow for such a course through all 12-13 modules, perhaps some of the history of MSP courses at the University of Rochester, and general Head TA guidelines that will make the role manageable to even someone new to MSP. 
 

\subsection{Git-repo}

\subsection{Resources}

\section{Course Flow}

\section{Duties}


\end{document}